---
output:
  word_document: default
  html_document: default
---

PRE-PROCESSING THE FINAL DATASET FOR ANALYSIS:

I)Creating drug classes, follow up duration related variables.
II) Adding residuals to 0 event studies
III) Filtering out studies:
  1. Removing HIV co-infection based studies
  2. Missing info
  3. < 6month follow-up
  4. Unpublished (already removed)

```{r message=FALSE, warning=FALSE, include=FALSE}
require(RCurl)
library('googlesheets4')
library(readr)
library(readxl)
# meta-analysis packages
library(meta)
library(metafor)
#library(metagen)
library(metasens) 
# graphics packages
library(tidyverse)
library(reshape)
library(doBy)
library(stringr)
library(ggpubr)
library(patchwork)
library(dplyr)
library(data.table)


setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data")
#D1: Cleaned data (see VL_data_clean.R for the steps): VL_Main (from Redcap) --> VL_clean uploaded to google sheets
#Continuous changes to the file: Missing numbers, corrections
#Pick up latest cleaned file from Google Sheets
#Download it and save the sheet. Read it here-->
data <-read_excel("VL_RelapseDataset_Review_1March.xlsx", sheet = "AllStudies")

data<-data[,c("pub_id", "Inc/Excluded" ,"redcap_repeat_instance",  "pub_year" , "st_region" ,"st_total_num" ,
                 "sa_intv1_drug" , "sa_intv1_dose_mgkg"  ,"sa_intv1_freq_discrete" ,  "sa_intv1_freq_new" , "sa_intv1_dura", "sa_int1_total_dose", 
                  "sa_intv2_drug" ,  "sa_intv2_dose_mgkg" , "sa_intv2_freq_discrete" ,  "sa_intv2_dura" ,
                   "sa_num_tx", "eff_arm_icure_num" , "eff_arm_relapse_num" ,  "me_hiv_yn",  
                    "relapse_match",  "initial_cure_match" , "initial_cure","relapse_6m","relapse_12m")   ]


length(unique(data$pub_id)) #160 studies: Only published studies. (Already filtered unpublished ones from the cleandata file (Drive))

#Additional variables from the vl_methods and vl_studydesign: Relapse definitions, severe cases inclusion, type if VL cases.

#D2: VL_SEVEREDESIGN

relapse_def<-  read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/VL_RelapseMethods.xlsx",  sheet = "Relapse_definition_method")
relapse_def$relapse_method_for_analysis <-tolower(relapse_def$relapse_method_for_analysis)
relapse_def<-relapse_def[,c("Tag","relapse_method_for_analysis")]


#D3
vl_sev <- read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/VL_StudyDesign.xlsx", 
    sheet = "disease_severity", col_types = c("skip", "numeric", "skip", "numeric", "skip", "text", "numeric", "skip", "text", "skip", "text"))
#Don't change order in the raw excel file

setDT(vl_sev)[, arm_no := rowid(tag)]
vl_sev$id<-paste0(vl_sev$tag,"_",vl_sev$arm_no)
vl_sev$tag<-NULL
vl_sev$Arm_ID<-NULL
vl_sev$arm_no <-NULL


#D4: VL_SAE (Taken from SAE paper)
vl_sae <- read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/VL_SAE.xlsx", sheet = "VL_SAEs_per_arm_04_12_2019", 
          col_types = c("skip", "skip", "skip",    "numeric", "skip", "numeric", "skip", "skip", "skip", "skip", "skip", "text",  "skip", "skip", "numeric", "numeric", "skip", "skip", "skip", "skip", "skip"))

vl_sae$id<-paste0(vl_sae$Tag,"_",vl_sae$Repeat.Instance )
vl_sae$Tag<-NULL
vl_sae$Repeat.Instance<-NULL

drug_cat <- read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/DrugCategories.xlsx", sheet = "drug_category")


#combining all variables in one df
#Unique ID for every study & arm
data$id<-paste0(data$pub_id,"_",data$redcap_repeat_instance)
df<-left_join(data,vl_sae,by='id')
df<-left_join(df,vl_sev,by="id")  
colnames(relapse_def)[1]<-"pub_id"
df<-left_join(df,relapse_def,by="pub_id")
 
df$tag<-NULL
df$Arm_ID<-NULL
df$arm_no<-NULL
length(unique(df$pub_id))
```


#2) Subsetting excluded studies

```{r}
rm(data)
rm(vl_sae)
rm(vl_sev)
rm(relapse_def)

data_all<-df
df<-subset(data_all,data_all$`Inc/Excluded`=="Inc")
length(unique(df$pub_id))
#131 left
```
Drug classifications: Main variable created for analysis: drugcat
```{r}
#Single drug or combination therapy. mono=1 for single drug
df$mono<-ifelse(is.na(df$sa_intv2_drug),1,0)

#Making new treatment name
df$drug<-ifelse(df$mono==1,df$sa_intv1_drug, paste0(df$sa_intv1_drug,' & ',df$sa_intv2_drug))

#Drug list
druglist<-unique(df$drug)

#Dosage of LamB?
#Use Freq_new as original dosage variable has missing info.
#Freq_new created after 11_25 version based on checkinh dose information manually

df$sd<-ifelse(df$sa_intv1_freq_new=="Single dose",1,
              ifelse(df$sa_intv1_freq_new=="Unknown",99,0))

#Variable dcat is for LamB regimens

df$dcat<-ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==1),"LamB SD Mono", #LamB single dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==1),"LamB SD Comb",#LamB single dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==0),"LamB MD Mono",#LamB multi dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==0),"LamB MD Comb",#LamB multi dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==1 & df$sd==99),"LamB UD Mono",#LamB ? dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==0 & df$sd==99),"LamB UD Comb",0))))))#LamB ? dose Combo



colnames(drug_cat)<-c("drug","drug_cat_others","Freq")
#Combining with formal list of drug categories
df<-left_join(df,drug_cat,by='drug')
df$Freq<-NULL
#Drugcat is final drug regimen variable
df$drugcat<-ifelse(df$dcat==0,df$drug_cat_others,df$dcat)


#Drug category list
drugcatlist<-unique(df$drugcat)

```


```{r}

df$relapse_measurement_time<-ifelse(df$relapse_match=="Match",180,
                                    ifelse(df$relapse_match=="NM",180,
                                           ifelse(df$relapse_match=="12monthinfo",360,
                                                  ifelse(df$relapse_match=="6-12monthinfo","180-360",NA))))

df$relapse_180<-ifelse(df$relapse_match=="Match",df$eff_arm_relapse_num,
                                    ifelse(df$relapse_match=="NM",df$relapse_6m,
                                           ifelse(df$relapse_match=="12monthinfo",df$relapse_6m,
                                                  ifelse(df$relapse_match=="6-12monthinfo",df$relapse_6m,NA))))


df$relapse_360<-ifelse(df$relapse_match=="12monthinfo",df$relapse_12m,
                                                  ifelse(df$relapse_match=="6-12monthinfo",df$relapse_12m,NA))
```


```{r}
#Converting to factors, changing group names.

df$cases_grouped<-as.factor(df$cases_grouped)
df$cases_grouped[is.na(df$cases_grouped)]<-"Unclear"
df$severe_ka_included[is.na(df$severe_ka_included)]<-"Unclear"
df$relapse_method_for_analysis<-as.factor(df$relapse_method_for_analysis)


df$failures<-df$sa_num_tx-df$initial_cure
df[,c("number_of_deaths","n_SAEs")]<-sapply(df[,c("number_of_deaths","n_SAEs")], as.numeric)
df<-as.data.frame(df)

```


```{r}

#Checking how many with rmt180 and rmt360==0
 
df_final<-df[,c('id','pub_id','st_region','drugcat', "sa_int1_total_dose",
                      "st_total_num",'sa_num_tx',"relapse_measurement_time",'initial_cure','relapse_180','relapse_360',
                      'cases_grouped','severe_ka_included','relapse_method_for_analysis', 'pub_year')]


setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data")
saveRDS(df_final,'VLRelapse_Dataset.RDS')

```








