Analysis and results:

#1. Initialization: Loading libraries, functions and data
```{r message=FALSE, warning=FALSE, include=FALSE}
    library(readr)
    library(readxl)
# meta-analysis packages
    library(meta)
    library(metafor)
    library(metasens) 
# graphics packages
    library(tidyverse)
    library(reshape)
    library(doBy)
    library(stringr)
    library(ggpubr)
    library(patchwork)
    library(dplyr)
    library(data.table)


source("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/MA_extract_functions.R")
df<-readRDS('C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/VLRelapse_MainDataset.RDS')


```

#2. General descriptive stats
1.	No. of studies by region and %
2.	No. of studies by follow-up duration, % (6 & 12)
3.	No. of studies by Relapse diagnosis method
4.	Total drug regimen and major ones

```{r}
#Total patients treated, cured and relapsed
df$relapse_total<-rowSums(df[,c('relapse_180','relapse_360')],na.rm = TRUE)
sum(df$sa_num_tx) #Treated
sum(df$initial_cure) #initially cured
sum(df$relapse_180,na.rm = TRUE)#Relapsed at 6month
sum(df$relapse_360,na.rm = TRUE)#Relapsed at 12 months
sum(df$relapse_total,na.rm = TRUE)#Relapsed total


#1.	No. of studies by region and %
df %>% group_by(st_region) %>%summarise(pub_count= n_distinct(pub_id))
df %>% group_by(st_region) %>%summarise(pub_prop= n_distinct(pub_id)/(0.01*length(unique(df$pub_id))))
df %>% group_by(st_region) %>%summarise(arm_count= n_distinct(id))  


#2.	No. of studies by follow-up duration, % (6 & 12)
df %>% group_by(relapse_measurement_time) %>%summarise(count= n_distinct(pub_id))
#Study 82 is double counted as 1 arm had follow-up till 6 months and one till 12 months.
#7, 11, 88: Def cure at 8 & 9 months (not at 12 months)

#3.	No. of studies by Relapse diagnosis method
df %>% group_by(rel_diag) %>%summarise(pub_count= n_distinct(pub_id))
df %>% group_by(rel_diag) %>%summarise(pub_prop= n_distinct(pub_id)/(0.01*length(unique(df$pub_id))))

#4. No of studies By infection type
df %>% group_by(inf_type) %>%summarise(pub_count= n_distinct(pub_id))
df %>% group_by(inf_type) %>%summarise(pub_prop= n_distinct(pub_id)/(0.01*length(unique(df$pub_id))))

```


#3. Table 1: Estimates from Overall Meta anlaysis & by subgroups

##1) Overall
```{r include=FALSE}
#1. Overall estimate at 6 months and overall 

bias_pval<-NULL
cat_name<-"Overall-6m"
m<- metaprop(  data = df,  event =relapse_180,  n= initial_cure, method='GLMM',  sm = "PLOGIT",  hakn = TRUE, prediction=TRUE)
summary(m)


m_adj<-copas(m, gamma0.range=c(-2,5), gamma1.range=c(-1,2))
overall_est<-m_extract(m_adj,cat_name)

#Checking for bias using Egger's test and storing the values in bias_pval object
bias<-metabias(m,method.bias = "Egger")
bias_pval<-rbind(bias_pval,c(cat_name,bias$pval))
bias_pval<-as.data.frame(bias_pval)
table1<-overall_est
rm(m_adj,bias, overall_est)
```

```{r}

m_region<-update.meta(m, 
            byvar=st_region, 
            comb.random = TRUE,
            comb.fixed = F)

m_drug<-update.meta(m, 
            byvar=drugcat, 
            comb.random = TRUE,
            comb.fixed = F)

m_relapsemethod<-update.meta(m, 
            byvar=rel_diag, 
            comb.random = TRUE,
            comb.fixed = F)


m_casemix<-update.meta(m, 
            byvar=inf_type, 
            comb.random = TRUE, 
            comb.fixed = F)


m_decade<-update.meta(m, 
            byvar=decade, 
            comb.random = TRUE, 
            comb.fixed = F)
```

##2) By region

```{r message=FALSE, warning=FALSE, include=FALSE}
#1.2: By region at 6 months
region<-unique(df$st_region)


#Carrying meta analysis for all regions and storing them in mr1, mr2...
for (i in 1:6){
  df_tmp<-subset(df,df$st_region==region[i])
               m_tmp<- metaprop(data = df_tmp,  event =relapse_180,  n=initial_cure,  
                                method="GLMM",sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)
               assign(paste0("m_reg",i),m_tmp)}

rm(m_tmp,df_tmp)


m_adj<-copas(m_reg1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
cat_name=m_adj$x$data$st_region[1]
or1<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg1,method.bias = "Egger")
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
#p-value = 0.0004

m_adj<-copas(m_reg2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
cat_name=m_adj$x$data$st_region[1]
or2<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg2,method.bias = "Egger",k.min = 5)
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
#p=0.11


m_adj<-copas(m_reg3, gamma0.range=c(-2,5), gamma1.range=c(0,2))
#m_unadj<-m_reg3
cat_name=m_adj$data$st_region[1]
or3<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg3,method.bias = "Egger")
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
# p-value = 0.339
cat_name=m_adj$x$data$st_region[1]
or3<-m_extract(m_adj,cat_name)
metabias(m_reg3,method.bias = "Egger")

###

m_adj<-copas(m_reg4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
cat_name=m_adj$x$data$st_region[1]
or4<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg4,method.bias = "Egger",k.min=5)
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
#0.038

m_adj<-copas(m_reg5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
cat_name=m_adj$x$data$st_region[1]
or5<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg5,method.bias = "Egger",k.min=5)
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
# p=0.33


m_adj<-copas(m_reg6, gamma0.range=c(-2,5), gamma1.range=c(0,2))
cat_name=m_adj$x$data$st_region[1]
or6<-m_extract(m_adj,cat_name)
pv<-metabias(m_reg6,method.bias = "Egger",k.min=5)
bias_pval<-rbind(bias_pval,c(cat_name,pv$p.value))
rm(pv)
# (k=7) too small to test for small study effects

table1<-rbind(table1, or1, or2,or3, or4, or5, or6)
rm(or1,or2,or3, or4, or5, or6)
rm(m_reg1, m_reg2, m_reg3, m_reg4, m_reg5, m_reg6)
rm(m_adj, m)
```




##3) By drug regimen
```{r include=FALSE}
#1.3: By drug
drug<-unique(df$drugcat)
#Carrying meta analysis for all regions nad storing them in mr1, mr2...
for (i in 1:17){
    df_tmp<-subset(df, df$drugcat== drug[i])
          m_tmp<- metaprop(data = df_tmp,  event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)
               bias<-metabias(m_tmp,method.bias = "Egger",k.min=5)
               assign(paste0("m_drug",i),m_tmp)
               bias_pval<-rbind(bias_pval,c(drug[i],bias$p.value))
               rm(bias,m_tmp,df_tmp)
               }
               


m_adj<-copas(m_drug1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od1<-m_extract(m_adj,cat_name)
metabias(m_drug1,method.bias = "Egger")
# k small


m_adj<-copas(m_drug2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od2<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug2,method.bias = "Egger")
# p-value = 0.0815


m_adj<-copas(m_drug3, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od3<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug3,method.bias = "Egger")
# p-value = 0.8776



m_adj<-copas(m_drug4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od4<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug4,method.bias = "Egger",k.min=5)
# p-value = k=9 too small


#m_adj<-copas(m_drug5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
#m_unadj<-m_drug5
#cat_name=m_unadj$data$drugcat[1]
#od5<-m_extract0(m_unadj,cat_name)
#rm(m_unadj)
#metabias(m_drug5,method.bias = "Egger")

m_adj<-copas(m_drug5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od5<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug5,method.bias = "Egger")


m_adj<-copas(m_drug6, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od6<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug6,method.bias = "Egger")
# p-value = 0.0053



m_adj<-copas(m_drug7, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od7<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug7,method.bias = "Egger")
# p-value = k small



m_adj<-copas(m_drug8, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od8<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug8,method.bias = "Egger")
# p-value = 0.229


m_adj<-copas(m_drug9, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od9<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug9,method.bias = "Egger")
# p-value = 0.0028


m_adj<-copas(m_drug10, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od10<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug10,method.bias = "Egger")
# p-value =  0.7672



m_adj<-copas(m_drug11, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od11<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug11,method.bias = "Egger")
# p-value =  k small


m_adj<-copas(m_drug12, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od12<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug12,method.bias = "Egger", k.min=5)
# p-value =  k small

m_adj<-copas(m_drug13, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od13<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug13,method.bias = "Egger")
# p-value =  0.34


m_adj<-copas(m_drug14, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od14<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug14,method.bias = "Egger")
# p-value = k small

m_adj<-copas(m_drug15, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$drugcat[1]
od15<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_drug15,method.bias = "Egger")
# p-value =  0.94

#m_adj<-copas(m_drug5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_unadj<-m_drug17
cat_name=m_unadj$data$drugcat[1]
od17<-m_extract0(m_unadj,cat_name)
rm(m_unadj)
metabias(m_drug17,method.bias = "Egger")
# p-value = k small

table1<-rbind(table1, od1, od2, od3, od4,od5,  od6, od7, od8, od9, od10, od11, od12, od13, od14, od15, od17)
rm(m_drug1, m_drug2, m_drug3, m_drug4, m_drug5, m_drug6, m_drug7, m_drug8, m_drug9, m_drug10, m_drug11, m_drug12, m_drug13, m_drug14, m_drug16,m_drug17, m_drug15,  m_drug17)

rm(od1, od2, od3, od4, od5, od6, od7, od8, od9, od10, od11, od12, od13, od14, od15, od17)
#Drug 16& 17: No. of studies too low
```


##4) Relapse diagnosis method

```{r include=FALSE}
#1.3: Relapse Diagnosis Method

relapsediagmethod<-unique(as.character(df$rel_diag))
#Carrying meta analysis for all regions and storing them in mr1, mr2...
for (i in 1:5){
   rel<-relapsediagmethod[i]
   df_tmp<-subset(df,df$rel_diag==rel)
               m_tmp<- metaprop(data = df_tmp,  event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)
               bias<-metabias(m_tmp,method.bias = "Egger",k.min=5)
               
               bias_pval<-rbind(bias_pval,c(rel,bias$p.value))
               assign(paste0("m_rel",i),m_tmp)

               rm(bias,m_tmp)}



m_adj<-copas(m_rel1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$rel_diag[1]
orel1<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_rel1,method.bias = "Egger")
# p-value < 0.0001


m_adj<-copas(m_rel2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$rel_diag[1]
orel2<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_rel2,method.bias = "Egger")
# p-value =0.148


m_adj<-copas(m_rel3, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
cat_name=m_adj$x$data$rel_diag[1]
orel3<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_rel3,method.bias = "Egger", k.min=5)

#Value changes a lot with gamma0! ( 4 to 5)


#m_adj<-copas(m_rel4, gamma0.range=c(-1,5), gamma1.range=c(0,3))
#Only 2 arms (1 study) with molecular diagnostic method
m_unadj<-m_rel4
cat_name=m_unadj$data$rel_diag[1]
orel4<-m_extract0(m_unadj,cat_name)
rm(m_unadj)

m_adj<-copas(m_rel5, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
cat_name=m_adj$x$data$rel_diag[1]
orel5<-m_extract(m_adj,cat_name)
rm(m_adj)

table1<-rbind(table1, orel1, orel2, orel3, orel4,orel5)
rm(m_rel1, m_rel2, m_rel3, m_rel4,m_rel5)
rm(orel1, orel2, orel3, orel4,orel5)
rm(relapsediagmethod)


```




##5) Infection type

```{r include=FALSE}
casemix<-unique(as.character(df$inf_type))

for (i in 1:4){
  cm<-casemix[i]
   df_tmp<-subset(df,df$inf_type==cm)
              m_tmp<- metaprop(data = df_tmp,  event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)
              
               bias<-metabias(m_tmp,method.bias = "Egger",k.min=5)
               bias_pval<-rbind(bias_pval,c(cm,bias$p.value))
               
               assign(paste0("m_case",i),m_tmp)
               rm(m_tmp,df_tmp,bias)}



m_adj<-copas(m_case1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$inf_type[1]
ocase1<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_case1,method.bias = "Egger")
cat_name
# p-value = 0.0002



m_adj<-copas(m_case2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$inf_type[1]
ocase2<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_case2,method.bias = "Egger")
cat_name

# p-value <0.001


m_adj<-copas(m_case3, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
cat_name=m_adj$x$data$inf_type[1]
ocase3<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_case3,method.bias = "Egger")
cat_name

#p=0.02
m_adj<-copas(m_case4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$inf_type[1]
ocase4<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_case4,method.bias = "Egger")
cat_name

# p-value = 0.85


table1<-rbind(table1, ocase1, ocase2, ocase3, ocase4)
rm(m_case1, m_case2, m_case3, m_case4)
rm(ocase1, ocase2, ocase3, ocase4)



#Exploring unresponsive VL cases:

df1<-subset(df, df$inf_type=="Unresponsive VL")
```



##6) Decade

```{r include=FALSE}

m<- metaprop(data=df,event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)

m_decade<-update.meta(m, 
            byvar=decade, 
            comb.random = TRUE, 
            comb.fixed = F)


#p=0.0037
decade<-unique(df$decade)

for (i in 1:4){
 dec<-decade[i]
   df_tmp<-subset(df,df$decade==dec)
               m_tmp<- metaprop(data = df_tmp,  event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)
               assign(paste0("m_dec",i),m_tmp)
               bias<-metabias(m_tmp,method.bias = "Egger",k.min=5)
               bias_pval<-rbind(bias_pval,c(dec,bias$p.value))
               
               rm(m_tmp,df_tmp,bias)}



m_adj<-copas(m_dec1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$decade[1]
odec1<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_dec1,method.bias = "Egger")
# p-value = 0.064



m_adj<-copas(m_dec2, gamma0.range=c(-3,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$decade[1]
odec2<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_dec2,method.bias = "Egger")
# p-value < 0.0001


m_adj<-copas(m_dec3, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
cat_name=m_adj$x$data$decade[1]
odec3<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_dec3,method.bias = "Egger")
# p-value = 0.0037

#Value changes a lot with gamma0! ( 4 to 5)

m_adj<-copas(m_dec4, gamma0.range=c(-3,5), gamma1.range=c(0,2))
m_adj
cat_name=m_adj$x$data$decade[1]
odec4<-m_extract(m_adj,cat_name)
rm(m_adj)
metabias(m_dec4,method.bias = "Egger")
# p-value = 0.0014


table1<-rbind(table1, odec1, odec2, odec3, odec4)
rm(m_dec1, m_dec2, m_dec3, m_dec4)
rm(odec1, odec2, odec3, odec4)

```



#4. Table 1: 6 month vs 12 month
Focus on 19 studies with follow up duration of more than 6 months
(make changes to Study #11)

```{r message=FALSE, warning=FALSE, include=FALSE}
#df_12mfu<-subset(df,!is.na(df$relapse_360))
df_12mfu<-subset(df,df$relapse_measurement_time=="360")
#or remove 180-360 studies? (8 arms)

df_12mfu %>% group_by(st_region) %>% summarise(n_distinct(pub_id))
length(unique(df_12mfu$pub_id))

df_12mfu$relapse_total<-df_12mfu$relapse_180+df_12mfu$relapse_360

m_overall<- metaprop(data =df_12mfu,event =relapse_total,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)

m_360<- metaprop(data =df_12mfu,event =relapse_360,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)

m_180<- metaprop(data =df_12mfu,event =relapse_180,  n=initial_cure, 
                           method="GLMM", sm = "PLOGIT", hakn = TRUE,  prediction=TRUE)


forest(m_360)
m_adj<-copas(m_overall, gamma0.range=c(-2,5), gamma1.range=c(0,2))
metabias(m_overall,method.bias = "Egger")
cat_name<-"Long FU Overall"
o1<-m_extract(m_adj,cat_name)


m_adj<-copas(m_360, gamma0.range=c(-3,6), gamma1.range=c(-1,3))
m_adj
metabias(m_360,method.bias = "Egger")
cat_name<-"Long FU 12m"
o2<-m_extract(m_adj,cat_name)

m_adj<-copas(m_180, gamma0.range=c(-2,5), gamma1.range=c(0,2))
metabias(m_180,method.bias = "Egger")
cat_name<-"Long FU 6m"
o3<-m_extract(m_adj,cat_name)

results_6vs12<-rbind(o1,o2,o3)

events1<-df_12mfu %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(relapse_total, na.rm = TRUE), 
    n_cured	= sum(initial_cure),
    n_totfu= sum(sa_num_tx))

events2<-df_12mfu %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(relapse_360, na.rm = TRUE), 
    n_cured	= sum(initial_cure),
    n_totfu= sum(sa_num_tx))

events3<-df_12mfu %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(relapse_180, na.rm = TRUE), 
    n_cured	= sum(initial_cure),
    n_totfu= sum(sa_num_tx))

n_event<-c(events1[1,2], events2[1,2],events3[1,2])
results_6vs12$relapse<-n_event
table1<-rbind(table1,results_6vs12)

Store_table1<-table1
```

#5. Table 1 formatting
```{r}

cols.num <- c( "est0","lb0","ub0","est","lb","ub","i2","i2lb","i2ub","pi_lb","pi_ub")
table1[cols.num] <- sapply(table1[cols.num],as.numeric)
table1[, cols.num] <- lapply(table1[, cols.num, drop = FALSE],  function(x) x * 100)

table1[, cols.num] <- lapply(table1[, cols.num, drop = FALSE],
                             function(x) round(x,1))

table1$tausq<-round(table1$tausq,1)
drugcat_names <-read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/DrugCategories.xlsx", 
    sheet = "drug cat full names")

colnames(table1)[which(colnames(table1) == 'name')] <- 'drugcat'
table1<-left_join(table1,drugcat_names,by="drugcat")
table1$name<-ifelse(is.na(table1$`Drug Category`),table1$drugcat,table1$`Drug Category`)



table1$unadj<-with(table1,paste0(est0,"% [95% CI: ",lb0,"%-",ub0,"%]"))
table1$adj<-with(table1,paste0(est,"% [95% CI: ",lb,"%-",ub,"%]"))
table1$pred<-with(table1,paste0(pi_lb,"% - ",pi_ub,"%"))
table1$tcr<-with(table1,paste0(tot,"/",cured,"/",relapse))

table1<-table1[,c("name","arms","tcr","unadj","tausq","i2","adj","pred")]

write.csv(table1,'C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Results/Table1_0329.csv')

```

#6. Table 4: Longer follow-up studies

```{r}
library(tidyr)
library(readr)
library(tidyselect)

library(tidyverse)
library(reshape)
library(doBy)
library(stringr)
library(ggpubr)
library(patchwork)
library(dplyr)
library(data.table)

studies12m<- df_12mfu %>% group_by(pub_id) %>% 
                summarise(n_treated=sum(sa_num_tx), initial_cure=sum(initial_cure),  
                          relapse_total = sum(relapse_total),relapse_180=sum(relapse_180),relapse_360=sum(relapse_360))


prop_180<- metaprop(data=studies12m,event = relapse_180, n = initial_cure)

# create a data frame with the study ID, proportion, and 95% confidence interval
result_180 <- data.frame(
  study_id = prop_180$data$pub_id,
  proportion = round((exp(prop_180$TE)/(1+exp(prop_180$TE)))*100,1),
  lower_CI = round((prop_180$lower*100),1),
  upper_CI = round((prop_180$upper*100),1))




result_180$prop_6m<-with(result_180,paste0(proportion,"% [95% CI: ",lower_CI,"%-",upper_CI,"%]"))



prop_360<- metaprop(data=studies12m,event = relapse_360, n = initial_cure)

# create a data frame with the study ID, proportion, and 95% confidence interval
result_360 <- data.frame(
  study_id = prop_360$data$pub_id,
  proportion = round((exp(prop_360$TE)/(1+exp(prop_360$TE)))*100,1),
  lower_CI = round((prop_360$lower*100),1),
  upper_CI = round((prop_360$upper*100),1))




result_360$prop_12m<-with(result_360,paste0(proportion,"% [95% CI: ",lower_CI,"%-",upper_CI,"%]"))



studies12m$prop_360<-result_360$prop_12m
studies12m$prop_180<-result_180$prop_6m


studies12m<-left_join(studies12m,df_12mfu[,c("pub_id","drugcat")],by='pub_id')
drugcat_names <-read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Data/DrugCategories.xlsx", 
    sheet = "drug cat full names")

studies12m<-left_join(studies12m,drugcat_names,by="drugcat")
studies12m$drugcat<-NULL
studies12m$drugcat1<-NULL
write.csv(studies12m,"C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/VL/Analysis/VL-Relapses/Results/Table4.csv")




```

```{r}

df$st_type<-ifelse(df$st_allocation=="Randomised","R","NR")
df %>% group_by(st_type) %>%summarise(pub_count= n_distinct(pub_id))

m_type<-update.meta(m, 
            byvar=st_type, 
            comb.random = TRUE,
            comb.fixed = F)


```


```{r}
library('lme4')
df$def_cure<-df$initial_cure-df$relapse_180
df$pub_year_scaleed<-df$pub_year/1000
df$inf_type<-relevel(df$inf_type,ref="Primary")
model1<- glmer(cbind(relapse_180,def_cure) ~ inf_type +pub_year+ (1 | id), family = binomial, data = df)
summary(model1)
ci<-summary(model1)$coefficients[4,1]+qnorm(c(0.025,0.5,0.975))*summary(model1)$coefficients[4,2]
round(exp(ci),2)


```

